Understanding the impacts of video-guided activities on parent-child interaction

### 2021-01-08 paper/manuscript.Rmd
observer bias

### Procedure
After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of approximately three minutes.[^2]
In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.

[^2]: Based on piloting, we estimated these activities would would only require three minutes to complete.

@@

@@

>>>>

### Procedure
After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of approximately three minutes.[^2]
In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.^[Based on piloting, we estimated these activities would would only require three minutes to complete.]

@@

Experimenters were aware of the condition structure of the experiment and condition assignment of parents but made no comments or other intervention once the parent-child interaction began.

@@

We assume that, because parents knew that they were being videotaped, they might alter their behaviors in response to the presence of the camera. 
However, we assume that these alterations should be evenly distributed between conditions; thus inferences regarding condition differences in interaction should be unaffected by this factor.
